The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-22 project/paper/properties.tex
Tweaked wording about jacobian.
Tweak to properties.
Derived variance, changed references to match.

The skew-normal was first introduced by \citet{o'hagan} and was most notably
developed by \citet{azzalini-1985}. Some of its other basic properties, given
by \citet{pewsey}, are

\begin{align}
  E(Y) &= \mu + b \delta \sigma, \nonumber \\
  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-basic-properties} \\
  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \nonumber \\
  Var(Y) &= \sigma^2 (1 - b^2 \delta^2), \nonumber
\end{align}

where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
\lambda^2}}$.

@@

\begin{align*}
  f(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
\end{align*}

@@

  On $A_1$: $y = -x \Ra x = -y$ and the Jacobian $\J = \left| \frac{dx}{dy}
  \right| = |-1| = 1$, yielding

@@

  Similarly, on $A_2$: $y = x \Ra x = y$ and the Jacobian $\J = \left|
  \frac{dx}{dy} \right| = |1| = 1$, yielding

>>>>

The skew-normal was first introduced by \citet{o'hagan} and was most notably
developed by \citet{azzalini-1985}.

The skew-normal's first three moments about the origin, given by
\citet{pewsey}, are

\begin{align}
  E(Y) &= \mu + b \delta \sigma, \nonumber \\
  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-moments-about-origin} \\
  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \nonumber
\end{align}

where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
\lambda^2}}$. Using these facts, we can easily derive $Var(Y)$:

\begin{align}
  Var(Y) &= E(Y^2) - [E(Y)]^2 \nonumber \\
  &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 - (\mu + b \delta \sigma)^2 \nonumber \\
  &= \cancel{\mu^2} + \cancel{2b \delta \mu \sigma} + \sigma^2 - \cancel{\mu^2} - \cancel{2b \delta \mu \sigma} - b^2 \delta^2 \sigma^2 \nonumber \\
  &= \sigma^2 - b^2 \delta^2 \sigma^2 \nonumber \\
  &= \sigma^2 (1 - b^2 \delta^2). \label{eq:sn-variance}
\end{align}

@@

\begin{align*}
  f(x|\mu, \sigma, \lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
\end{align*}

@@

  On $A_1$: $y = -x \Ra x = -y$ and Jacobian $\J = \left| \frac{dx}{dy} \right|
  = |-1| = 1$, yielding

@@

  Similarly, on $A_2$: $y = x \Ra x = y$ and Jacobian $\J = \left|
  \frac{dx}{dy} \right| = |1| = 1$, yielding
